Proyecto Final para la obtención del título: Ingeniero en Informática \tabularnewline \large Future Virtual Particle Method for Pedestrian Navigation

### 2015-06-09 doc/informe/informe.tex
agrego grafico para room escape - SFM. renombro carpeta room_evacuation a flow (ya que asi se usa en el informe). Correcciones varias para el informe.

\begin{abstract}
% Pedestrians are modeled as objects affected by repulsive and attractive forces in the Social Force Model (SFM). 
This paper presents an avoidance collision method based in pedestrian self
governed decisions, by calculating the position of every pedestrian
in the future, a given pedestrian can adjust his velocity vector to
avoid collisions instead of being affected by a repulsive force. \\
The model was tested using three different scenarios and compared 
against the Social Force Model obtaining more natural navigation,
reduced number of collisions, increased average
speed and reduced average deviation angle of navigating pedestrians.
\textbf{keywords:} pedestrian, collision avoidance, future virtual
particle, force model.
\end{abstract}

@@

    The average pedestrian flow ($Q_avg$) was taken by averaging the results of $5$ simulations for each configuration.\\
    The results are shown on fig. \ref{fig:room-flow-100}, fig. \ref{fig:room-flow-150} and fig. 
    \ref{fig:room-flow-200}.

    \begin{figure}[H]
        \begin{centering}
        \includegraphics[scale=0.2]{pics/flow/12door} 
        \par\end{centering}
        \caption{\label{fig:room-flow-100}Room evacuation with $1.2$ $[m]$ door}
    \end{figure}

    \begin{figure}[H]
        \begin{centering}
        \includegraphics[scale=0.2]{pics/flow/15door} 
        \par\end{centering}
        \caption{\label{fig:room-flow-150}Room evacuation with $1.5$ $[m]$ door}
    \end{figure}

    \begin{figure}[H]
        \begin{centering}
        \includegraphics[scale=0.2]{pics/flow/18door} 
        \par\end{centering}
        \caption{\label{fig:room-flow-200}Room evacuation with $1.8$ $[m]$ door}
    \end{figure}

    The escape flow for each configuration was calculated using octave's $polyfit$ using a 
    grade $1$ polygon and the slopes for each door size are as follows:

    \begin{table}[H]
        \begin{centering}
        \begin{tabular}{|c|c|c|c|}
        \hline 
        N \textbackslash{} Door size & $1.2$ & $1.5$ & $1.8$\tabularnewline
        \hline 
        \hline 
        $100$ & $1.02$ & $1.05$ & $1.05$\tabularnewline
        \hline 
        $150$ & $1.17$ & $1.18$ & $1.18$\tabularnewline
        \hline 
        $200$ & $1.20$ & $1.22$ & $1.23$\tabularnewline
        \hline 
        \end{tabular}
        \caption{Escape room configurations \label{tbl:room-runs}}
        \end{centering}
    \end{table}

@@

    Pedestrians can adjust their desired velocity at will, based on the
    data they perceive. We proposed a model that calculates the desired
    velocity of the social force model by conceptually moving the social
    force into the near future (FVP). The results look more natural than
    the original SFM and have been validated with experimental data. We
    used real-life metrics to validate our model, the results show that
    our model resembles reality with high fidelity. The proposed model
    produces a more natural navigation, but, at high densities, this isn't
    true, we still need further analysis of this scenario to adjust our
    model for both cases. \\
    In future work, the paths our virtual pedestrians
    may need to be compared and validated with real-life pedestrians
    paths to complement the use of metrics for the mean of pedestrians.
    Parameters should be re validated with more metrics and analyzed in
    even more detail. \\
    % It is important to notice that we have successfully removed the 
    % (undesired) social force from the original model and replacing it  
    % with the proposed changes, we were able reproduce real life results.
\newpage{}

>>>>

\begin{abstract}
% Pedestrians are modeled as objects affected by repulsive and attractive forces in the Social Force Model (SFM). 
This paper presents an avoidance collision method based in pedestrian self
governed decisions, by calculating the position of every pedestrian
in the future, a given pedestrian can adjust his velocity vector to
avoid collisions instead of being affected by a repulsive force. \\
The model was tested using three different scenarios and compared 
against the Social Force Model obtaining more natural navigation,
reduced number of collisions, increased average
speed and reduced average deviation angle of navigating pedestrians. \\
\textbf{keywords:} pedestrian, collision avoidance, future virtual
particle, force model.
\end{abstract}

@@

    The average pedestrian flow ($Q_avg$) was taken by averaging the results of $5$ simulations for each configuration.\\
    The results for the scenario with a door size of $1.5$ $[m]$ are shown on fig. \ref{fig:room-flow-150}:

    %\begin{figure}[H]
    %    \begin{centering}
    %    \includegraphics[scale=0.2]{pics/flow/12door} 
    %    \par\end{centering}
    %    \caption{\label{fig:room-flow-100}Room evacuation with $1.2$ $[m]$ door}
    %\end{figure}

    \begin{figure}[H]
        \begin{centering}
        \includegraphics[scale=0.2]{pics/flow/15door} 
        \par\end{centering}
        \caption{\label{fig:room-flow-150}FVPM - Room evacuation with $1.5$ $[m]$ door}
    \end{figure}

    For the same scenario, the escape flow when using the SFM model is shown on fig. \ref{fig:sfm-room-flow-15}

    \begin{figure}[H]
        \begin{centering}
        \includegraphics[scale=0.2]{pics/flow/sfm/sfm15door} 
        \par\end{centering}
        \caption{\label{fig:sfm-room-flow-15}SFM - Room evacuation with $1.5$ $[m]$ door}
    \end{figure}

    %\begin{figure}[H]
    %    \begin{centering}
    %    \includegraphics[scale=0.2]{pics/flow/18door} 
    %    \par\end{centering}
    %    \caption{\label{fig:room-flow-200}Room evacuation with $1.8$ $[m]$ door}
    %\end{figure}

    The escape flow for each door configuration for the FVPM was calculated using octave's 
    $polyfit$ using a grade $1$ polygon and the slopes for each door size are as follows:

    \begin{table}[H]
        \begin{centering}
        \begin{tabular}{|c|c|c|c|}
        \hline 
        Door size \textbackslash{} N & $100$ & $1.5$ & $200$\tabularnewline
        \hline 
        \hline 
        $1.2$ & $1.02$ & $1.05$ & $1.05$\tabularnewline
        \hline 
        $1.5$ & $1.17$ & $1.18$ & $1.18$\tabularnewline
        \hline 
        $1.8$ & $1.20$ & $1.22$ & $1.23$\tabularnewline
        \hline 
        \end{tabular}
        \caption{Escape room configurations \label{tbl:room-runs}}
        \end{centering}
    \end{table}

@@

    Pedestrians can adjust their desired velocity at will, based on the
    data they perceive. We proposed a model that calculates the desired
    velocity of the social force model by conceptually moving the social
    force into the near future (FVP). The results look more natural than
    the original SFM and have been validated with experimental data. We
    used real-life metrics to validate our model, the results show that
    our model resembles reality with high fidelity. The proposed model
    produces a more natural navigation, but, at high densities, this isn't
    true, we still need further analysis of this scenario to adjust our
    model for both cases. \\
    In future work, the paths our virtual pedestrians
    may need to be compared and validated with real-life pedestrians
    paths to complement the use of metrics for the mean of pedestrians.
    Parameters should be re validated with more metrics and analyzed in
    even more detail. \\
    % It is important to notice that we have successfully removed the 
    % (undesired) social force from the original model and replacing it  
    % with the proposed changes, we were able reproduce real life results.
    % The presented model was able to reproduce different number of pedestrians
    % leaving a room with different door sizes and showing that the exit flow
    % dos not depend on the number of pedestrians (in contrast to the SFM model)
\newpage{}
